### 2020-09-08 ART_Krzanowski/Krzanowski-PU.tex
Authors' and editorial corrections added

 Similar opinions by scientists, philosophers, and engineers have been voiced in most of the current discussions about information. Indeed, the concept of epistemic information has seen many incarnations, so there is no single definition that is acceptable to everyone or even to some nebulous majority.\footnote{The number of supporters actually does not matter, because in philosophy, ideas are not selected through democratic voting. Quite often, the ideas rejected by the majority actually contain the truth.} Take for example, Bar-Hiller and Carnap 

@@

&
Keith Devlin
%\label{ref:RNDmZpBnyGuy5}(1991)
\parencite*[][]{devlin_logic_1991}%
 &
``a fundamental form of information of relevance to that agent (a cognitive agent) is information of the form: Objects a1,…,an, have/have not property P.''\\
&
Claude Shannon
%\label{ref:RNDq5JwpFhRZV}(1948)
\parencite*[][]{shannon_mathematical_1948} %
 and other models related to Hartley-Shannon-Weaver's entropy of information &
H(X) (entropy of information in the TOC)\\
&
Solomonov \parencite*[][]{solomonoff_algorithmic_2010},
Kolmogorov \parencite*[][]{kolmogorov_1965}, %
%\label{ref:RND61d5QwkFKo}(1965; 1968),
 Chaitin \parencite*{chaitin_algorithmic_1987} &
String-complexity measures based on the UTM model\\
&
Fisher and Klir
%\label{ref:RND0hntx8ruul}(1988)
\parencite*[][]{klir_fuzzy_1988} %
 Models &
Statistical measures\\
\caption{comparison of selected epistemic concepts for information.}\label{tab2-krza}
\end{longtable}
\end{small}
%Table 2. A comparison of selected epistemic concepts for information.

@@

Epistemic information does not recognize the presence of ontological information, yet it cannot disregard the physical reality and the physical stimuli that forms a large source of epistemic information. Thus, in the definitions for epistemic information, we find data, physical signals, infons,\footnote{See, for example, the work of Stonier
%\label{ref:RNDejACLRHHLa}(1990),
\parencite*[][]{stonier_information_1990}, %
 Devlin 
%\label{ref:RNDNoRdVXnlNm}(1991),
\parencite*[][]{devlin_logic_1991}, %
 Floridi 
%\label{ref:RNDZ1SPaMhiYj}(2010b),
\parencite*[][]{floridi_philosophy_2010}, %
 and Martinez and Sequoiah-Grayson 
%\label{ref:RNDCRuW3o26eO}(2016).
\parencite*[][]{martinez_logic_2016}. %
} or something else filling this gap (e.g., the GDI definition of 
%\label{ref:RNDjuKQR1oy0q}(Floridi, 2010b)
\parencite[][]{floridi_philosophy_2010}%
).Simply speaking, the concept of epistemic information tends to disregard its physical basis. Thus, epistemic information, as it is, is not a complete description for the concept of information.

>>>>

 Similar opinions by scientists, philosophers, and engineers have been voiced in most of the current discussions about information. Indeed, the concept of epistemic information has seen many incarnations, so there is no single definition that is acceptable to everyone or even to some nebulous majority.\footnote{The number of supporters actually does not matter, because in philosophy, ideas are not selected through democratic voting. Quite often, the ideas rejected by the majority actually contain the truth.} Take for example, Bar-Hillel and Carnap 

@@

&
Keith Devlin
%\label{ref:RNDmZpBnyGuy5}(1991)
\parencite*[][]{devlin_logic_1991}%
 &
``a fundamental form of information of relevance to that agent (a cognitive agent) is information of the form: Objects a1,…,an, have/have not property P.''\\
&
Claude Shannon
%\label{ref:RNDq5JwpFhRZV}(1948)
\parencite*[][]{shannon_mathematical_1948} %
 and other models related to Hartley-Shannon-Weaver's entropy of information &
H(X) (entropy of information in the TOC)\\
&
Solomonov \parencite*[][]{solomonoff_algorithmic_2010},
Kolmogorov \parencite*[][]{kolmogorov_1965}, %
%\label{ref:RND61d5QwkFKo}(1965; 1968),
 Chaitin \parencite*{chaitin_algorithmic_1987} &
String-complexity measures based on the UTM model\\
&
Fisher and Klir
%\label{ref:RND0hntx8ruul}(1988)
\parencite*[][]{klir_fuzzy_1988} %
 Models &
Statistical measures\\
\caption{Comparison of selected epistemic concepts for information.}\label{tab2-krza}
\end{longtable}
\end{small}
%Table 2. A comparison of selected epistemic concepts for information.

@@

Epistemic information does not recognize the presence of ontological information, yet it cannot disregard the physical reality and the physical stimuli that forms a large source of epistemic information. Thus, in the definitions for epistemic information, we find data, physical signals, infons,\footnote{See, for example, the work of Stonier
%\label{ref:RNDejACLRHHLa}(1990),
\parencite*[][]{stonier_information_1990}, %
 Devlin 
%\label{ref:RNDNoRdVXnlNm}(1991),
\parencite*[][]{devlin_logic_1991}, %
 Floridi 
%\label{ref:RNDZ1SPaMhiYj}(2010b),
\parencite*[][]{floridi_philosophy_2010}, %
 and Martinez and Sequoiah-Grayson 
%\label{ref:RNDCRuW3o26eO}(2016).
\parencite*[][]{martinez_logic_2016}. %
} or something else filling this gap (e.g., the GDI definition of 
%\label{ref:RNDjuKQR1oy0q}(Floridi, 2010b)
\parencite[][]{floridi_philosophy_2010}%
). Simply speaking, the concept of epistemic information tends to disregard its physical basis. Thus, epistemic information, as it is, is not a complete description for the concept of information.
